---
title: "customer_time_series_multivariate"
output: html_notebook
---

## Import data processed in Python 
```{r}
library(readr)
library(forecast)
combined_clean <- read_csv("C:/Users/wangka3/Desktop/learning/R_exercise2/combined_clean.csv")
```

## The attempt to use ARIMAX
```{r}
train_data = combined_clean[1:15912, 5:58]
test_data = combined_clean[15913:17376, 5:58]
```

```{r}
model_cust = auto.arima(combined_clean$cust_168[1:15912], 
                        xreg = data.matrix(train_data))
```

```{r}
model_cust
```


```{r}
checkresiduals(model_cust)
```

### ARIMA does not capture seasonality well. Need to use another model.
```{r}
forecast_cust = forecast(model_cust, xreg = data.matrix(train_data))
(autoplot(forecast_cust))
```

## Now use tbats on msts 

### With seasonal periods equals to 24 hours and 24 * 7 = 168 hours.

* 15841 is the last row that has coherent time series data.
* 15913 is the first row of the test dataset.
* 17376 is the last row of the combined train/test dataset.
```{r}
cust <- msts(log(combined_clean$cust_168[1:15841] + 1), seasonal.periods=c(24,168))
model_cust <- tbats(cust)
(autoplot(forecast(model_cust, h = 17376 - 15841)))
```


```{r}
others <- msts(log(combined_clean$others_168[1:15841] + 1), seasonal.periods=c(24,168))
model_others <- tbats(others)
(autoplot(forecast(model_others, h = 17376 - 15841)))
```

## Try tbats on msts with covariates in xreg

```{r}
train_data = combined_clean[1:15841, 5:58]
test_data = combined_clean[15842:17376, 5:58]
```

Later I realised that the tbats model is based on ets which will not take advantage of the covariates.
https://robjhyndman.com/hyndsight/tbats-with-regressors/
```{r}
cust <- msts(log(combined_clean$cust_168[1:15841] + 1), seasonal.periods=c(24,168))
model_cust_improved <- tbats(cust, xreg = data.matrix(train_data))
```

```{r}
(autoplot(forecast(model_cust_improved, h = 17376 - 15841, xreg = test_data)))
```


## Try arima on msts with covariates in xreg

### With seasonal periods equals to 24 hours and 24 * 7 = 168 hours, this will be the best model as you will see. This version of the arima is better than the first attempt in that:

* time series is specified as multi seasonal
* time series is log transformed

### However, due to time limit, I will reduce the training dataset to only the most important feature, var_t, according to data visulisation, and its derived features, in order to reduce computation time.

Remember that:

* 15841 is the last row that has coherent time series data.
* 15913 is the first row of the test dataset.
* 17376 is the last row of the combined train/test dataset.
* Column 14 to 22 are var_t related features.

```{r}
train_data = combined_clean[1:15841, 14:22]
test_data = combined_clean[15842:17376, 14:22]
```

```{r}
cust <- msts(log(combined_clean$cust_168[1:15841] + 1), seasonal.periods=c(24,168))
others <- msts(log(combined_clean$others_168[1:15841] + 1), seasonal.periods=c(24,168))
```

```{r}
model_arimax_cust_with_covariates = auto.arima(cust, xreg = data.matrix(train_data))
```

```{r}
model_arimax_others_with_covariates = auto.arima(others, xreg = data.matrix(train_data))
```


## Prediction and Output

Again, remember that:

* 15841 is the last row that has coherent time series data.
* 15913 is the first row of the test dataset.
* 17376 is the last row of the combined train/test dataset.
```{r}
pred_cust = forecast(model_arimax_cust_with_covariates, h = 17376 - 15841, xreg = data.matrix(test_data))
autoplot(pred_cust)
result_cust = exp(pred_cust$mean) - 1
result_cust = result_cust[(15913 - 15841) : (17376 - 15841)]
```

```{r}
pred_others = forecast(model_arimax_others_with_covariates, h = 17376 - 15841, xreg = test_data)
autoplot(pred_others)
result_others = exp(pred_others$mean) - 1
result_others = result_others[(15913 - 15841) : (17376 - 15841)]
```

```{r}
output = combined_clean[15842:17376, 1:2]
output['cust_pred'] = result_cust
output['others_pred'] = result_others
output['total_cnt_pred'] = output$cust_pred + output$others_pred
```

```{r}
write.csv(output, file = "output.csv", row.names=FALSE)
```




